\documentclass[14pt]{beamer}
\input{include/pygments}

% \usepackage{beamerthemesplit} // Activate for custom appearance
\setbeamertemplate{navigation symbols}{}%remove navigation symbols


\newlength{\wideitemsep}
\setlength{\wideitemsep}{\itemsep}
\addtolength{\wideitemsep}{10pt}
\let\olditem\item
\renewcommand{\item}{\setlength{\itemsep}{\wideitemsep}\olditem}

\begin{document}

\title{Debuggable by Design}
\author{@ConradIrwin}
\date{\today}
\frame{\titlepage}

\frame
{
  \newcommand{\reversibledebuggingsoftware}{
   \footnote{``Reversible Debugging Software'', Cambridge 2013. \href{http://bit.ly/12ZygP3}{\color{blue}{bit.ly/12ZygP3}}}
  }

  \begin{itemize}
  \item<1-> Programmers spend 49.9\%\reversibledebuggingsoftware of their time debugging.
  \item<2-> This costs $ \$ 312,000,000,000 $ per year.
  \item<3-> Takes time away from fun stuff :).
  \end{itemize}
}

\frame
{
  \frametitle{Debugging 101}

  \begin{enumerate}
  \item[1.]<1-> Run the code, see that it's broken.
  \item[0.]<2-> Find and remove the bug.
  \item[1.]<3-> Run the code, see that it's fixed.
  \end{enumerate}
}

\frame
{
  \frametitle{Debuggable code lets you:}

  \begin{itemize}
  \item<1-> Run small fragments standalone.
  \item<2-> Tell whether code is running correctly.
  \item<3-> Infer where the problem is.
  \end{itemize}
}

\frame{
  \frametitle{Example of bad code in pry}

  \begin{itemize}
  \item Pry::Commands::Edit ``method name''
  \item --- \alert<4->{ Uses Pry::CodeObject to get a method }
  \item --- \alert<3->{ Invokes MethodPatcher(pry, method) }
  \item \hskip 1em --- \alert<2->{ Uses pry.edit to open code in vim }
  \item \hskip 1em --- \alert<1->{\em Evals the changed source code }
  \end{itemize}
}

\begin{frame}[fragile]
  \frametitle{Minimal example for bad code}
  \input{build/code/bad_minimal.rb}
\end{frame}

\frame{
  \frametitle{Refactoring we made}

  \begin{itemize}
  \item Pry::Commands::Edit ``method name''
  \item --- \alert<2->{ Uses Pry::CodeObject to get a method }
  \item --- { Uses pry.edit to open method.source in vim }
  \item --- \alert<2->{ MethodPatcher.new(method, source) }
  \item \hskip 1em --- \alert<1->{\em Evals the changed source code }
  \end{itemize}
}

\begin{frame}[fragile]
  \frametitle{Minimal example post-refactoring}
  \input{build/code/good_minimal.rb}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Minimal example in master today}
  \input{build/code/best_minimal.rb}
\end{frame}

\frame{

  \begin{itemize}

  \item All of this change was for step 1.
  \item ``Run the code, see it's broken''.
  \item ``Run the code, see it's fixed''.

  \end{itemize}

}

\frame{
  \frametitle{Make it easy to see if it worked}

}

\end{document}
